%----------------------------------------------------------------------------------------
%	SECTION TITLE
%----------------------------------------------------------------------------------------

\cvsection{Work Experience}

%----------------------------------------------------------------------------------------
%	SECTION CONTENT
%----------------------------------------------------------------------------------------

\begin{cventries}

\cventry
{Senior VP of Sales} % Job title
{Consolidated Glass Holdings, Inc.} % Organization
{Pedricktown, NJ} % Location
{Dec. 2017 - present} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item{Responsible for managing Invisiwall glass systems, including key personnel at Columbia Commercial Building products, J.E. Berkowitz, Solar Seal, and Dlubak Glass Corporation. }
\item{Branding Invisiwall shower door hardware: creating spec, data, and cut sheets with hardware catalogs.}
\item{Working directly with architects to specify the Invisiwall shower door system into their contract documents.}
\item{\textbf{Completed projects}}: Springwood Villages (Houston, TX), Lakeside Towers (Dallas, TX), L'Enfant Plaza Hotel (Washington DC), Westin Irving Convention Center Hotel (Irving, TX), Wheaton Library (Washington DC).
\item{\textbf{LOIs}}: Omni hotel (Oklahoma), 76 11th AV West \& East Towers (Manhattan, NY).
\end{cvitems}
}

%------------------------------------------------
\cventry
{President/CEO} % Job title
{Benowitz International Glass Products, LLC. } % Organization
{Henderson, NV} % Location
{Jul. 2016 - Dec. 2017} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item{Represented glass floaters, fabricators, shower door manufacturers, and Hardware manufactures.}
\item{Consulted a large hardware manufacture on an expansion plan.}
\item{\textbf{Completed projects}: 88th \& 90th Street (Manhattan, New York), Radisson Hotel (Manhattan, New York), Bosa Pacific Gate (San Diego, CA), Hern's Key Gig Harbor (Washington State), Grand Sierra Resort Hotel (Reno, NV), Hotel California (Las Vegas, NV), Home 2 suites (Las Vegas, NV), Wynn Hotel Louise Vuitton store (Las Vegas, NV), Largest T-Mobile store in the country (Las Vegas, NV), Embassy Suites Hotel (Washington DC), Oklahoma St. Francis Hospital.}
\end{cvitems}
}

\cventry
{Project Sales Manager} % Job title
{C.R. Laurence Co., Inc. } % Organization
{Vernon, CA} % Location
{Jul. 2010 - 2016} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Prepared competitive bids, negotiated, and closed sales of Transaction Hardware, Hospitality Hardware, Bullet Resistant Hardware, and Shower Door Hardware to glazing contractors throughout the US. Closed approximately \$20 million USD in sales per year.}
\item {Developed a company wide state-of-the-art quotation protocol.}
\item {Worked with project managers to complete projects in a timely fashion and ensured customer satisfaction.}
\item {Developed a 9 module training program for sales and follow up teams.}
\end{cvitems}
}

%------------------------------------------------    

\cventry
{Vice President Sales} % Job title
{Veltex Industries} % Organization
{Las Vegas, NV} % Location
{Jul. 2007 - Nov. 2009} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Developed an extensive market share by expanding and opening new accounts for glass and hardware packages for the hospitality industry in Las Vegas.}
\item {Closed both towers of the Cosmopolitan hotel, Hard Rock Hotel, and M Tower.}
\end{cvitems}
}

%------------------------------------------------

\cventry
{Sales Manager} % Job title
{Arizona Shower Doors} % Organization
{Las Vegas, NV} % Location
{Oct. 2001 - Jun. 2007} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Developed successful working relationships between AZ Shower Doors and glazing contractors in the Las Vegas area.}
\item {Grew the Las Vegas division from \$20000 to \$400000 per month in sales.}
\item{Got Arizona Shower Door's products into all of the Lowes in Las Vegas.}
\item{Projects included the MGM Grand Hotel, Montelago Village at Lake Las Vegas, and the Mandalay Bay.}
\end{cvitems} 
}

%------------------------------------------------

\cventry
{Owner/Manager} % Job title
{Rainbow Mirror and Designs} % Organization
{Phoenix, AZ} % Location
{Oct. 1986 - Sep. 2001} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Established and managed a retail mirror design and installation company for builders, home owners, and designers.}
\item{Hired, trained, and led a sales teams of 14.}
\item{Managed day-to-day operations including payroll and accounting functions.}
\item {Developed and maintained customer relationships; ensured staff compliance with company policies and practices.}
\end{cvitems}
}

%------------------------------------------------



\end{cventries}