%----------------------------------------------------------------------------------------
%	SECTION TITLE
%----------------------------------------------------------------------------------------

\cvsection{Talks}

%----------------------------------------------------------------------------------------
%	SECTION CONTENT
%----------------------------------------------------------------------------------------

\begin{cventries}

\cventry
{Interactive presentation} % Role
{University of Iowa, Center for Bioinformatics and Computational Biology} % Event
{Iowa City, Iowa} % Location
{Mar. 2016} % Date(s)
{ % Description(s)
\begin{cvitems}
\item { \href{https://prezi.com/kylgyfxdjz6o/the-beginning-of-a-world-without-genetic-disease/}{Protein Folding Reimagined: From Data Compression to Clinical Intervention} }
\end{cvitems}
}

\cventry
{Powerpoint presentation} % Role
{University of Iowa, Department of Molecular Physiology and Biophysics, Department of Biochemistry, Interdisciplinary Talk} % Event
{Iowa City, Iowa} % Location
{Jan. 2016} % Date(s)
{ % Description(s)
\begin{cvitems}
\item{\href{https://www.researchgate.net/publication/300823699_Protein_Folding_as_Data_Compression}{Protein Folding as Data Compression}}
\end{cvitems}
}

\cventry
{Powerpoint presentation} % Role
{Utah State University, Research Week} % Event
{Logan, Utah} % Location
{Mar. 2015} % Date(s)
{ % Description(s)
\begin{cvitems}
\item {\href{https://www.researchgate.net/publication/303565772_Centrality_Measures_of_Graphs_utilizing_Continuous_Walks_in_Hilbert_Space}{Centrality Measures of Graphs Utilizing Continuous Walks in Hilbert Space.}}
\end{cvitems}
}

\cventry
{Powerpoint presentation} % Role
{University of Alabama at Birmingham, Center for Nanoscale Materials and Biointegration REU Presentations} % Event
{Birmingham, Alabama} % Location
{Jul. 2014} % Date(s)
{ % Description(s)
\begin{cvitems}
\item {\href{https://www.researchgate.net/publication/276313026_Monitoring_Mitochondrial_Membrane_Potential_with_Mitoview_633_A_New_Molecular_Probe}{Monitoring the Mitochondrial Membrane Potential with Mitoview 633: A New Molecular Probe.}}
\end{cvitems}
}

%------------------------------------------------

\cventry
{White board presentation} % Role
{Utah State University, Mathematics Department, Discrete Mathematics Group} % Event
{Logan, Utah} % Location
{Sep. 2013} % Date(s)
{ % Description(s)
\begin{cvitems}
\item { \href{https://www.researchgate.net/publication/303565742_Approaching_the_Graph_Isomorphism_Problem_from_an_Information_Theoretic_Perspective}{Approaching the Graph Isomorphism Problem from an Information Theoretic Perspective.}}
\end{cvitems}
}

%------------------------------------------------



%------------------------------------------------



%------------------------------------------------



%------------------------------------------------



%------------------------------------------------

\end{cventries}